% Bibliographie

\begin{frame}[c]
  \frametitle{Bibliography}

\footnotesize
\setlength{\parindent}{-1em}
\setlength{\parskip}{0.5em}
~

\vfill
\tcite{Paulevé11} Loïc Paulevé. PhD thesis: \textit{Modélisation, Simulation et Vérification des Grands Réseaux de Régulation Biologique}, October 2011, Nantes, France

%\tcite{PMR10-TSE} Loïc Paulevé, Morgan Magnin, and Olivier Roux. \textit{Tuning Temporal Features within the Stochastic $\pi$-Calculus}. IEEE Transactions on Software Engineering, 37(6):858-871, 2011.

\tcite{PRM10-TCSB} Loïc Paulevé, Morgan Magnin, and Olivier Roux. \textit{Refining dynamics of gene regulatory networks in a stochastic $\pi$-calculus framework}. In Corrado Priami, Ralph-Johan Back, Ion Petre, and Erik de Vink, editors: Transactions on Computational Systems Biology XIII, volume 6575 of Lecture Notes in Computer Science, 171-191. Springer Berlin/Heidelberg, 2011.

\tcite{PMR12-MSCS} Loïc Paulevé, Morgan Magnin, and Olivier Roux. \textit{Static analysis of biological regulatory networks dynamics using abstract interpretation}. Mathematical Structures in Computer Science, in press, 2012.

%\tcite{PR10-CRAS} Loïc Paulevé and Adrien Richard. \textit{Topological Fixed Points in Boolean Networks}. Comptes Rendus de l'Académie des Sciences - Series I - Mathematics, 348(15-16):825 - 828, 2010.

\tcite{RCB08} Adrien Richard, Jean-Paul Comet, and Gilles Bernot. \textit{R. Thomas' logical method}, 2008. Invited at Tutorials on modelling methods and tools: Modelling a genetic switch and Metabolic Networks, Spring School on Modelling Complex Biological Systems in the Context of Genomics.

%\tcite{CMSB12} Maxime Folschette, Loïc Paulevé, Katsumi Inoue, Morgan Magnin, and Olivier Roux. \textit{Concretizing the Process Hitting into Biological Regulatory Networks}. In: Computational Methods in Systems Biology, Springer, 2012.

\vfill
\Large
\begin{flushright}
  \tval{Thank you}\hspace{1cm}~
\end{flushright}
\vfill

~

\end{frame}
